Functional oxide layers for electrical isolation and chemical passivation of steel substrates

### 2022-05-24 Thesis/chapter/03-theoretical-background.tex
start with ML

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Infrared Absorption and Spectroscopy}
\td{IR around page 45;
REFLECTIVITY? can also be used for determination of thickness p47\cite{Dumin1967}
}
\td{QUESTIONS: 
	how does a beam splitter work? 
	how does detector work? two different for UVVis and MIR
}

%%% WHAT? 
\Gls{ir} spectroscopy is a molecular spectroscopic method using interactions of \gls{ir} light (wavelengths $\lambda$ of \num{e-3} to \num{e-6}\m{}
or wave numbers $\bar{\nu}$ of 500 to \pcm{4000} ) with molecules. \cite{Schwedt2008}
In general, light is described as periodic \gls{em} wave 
which - in vacuum - moves with the speed of light ($c = \mps{299792458}$).
The relation of energy~$E$ of a photon, its frequency~$\nu$, wavelength~$\lambda$ and wave number~$\bar{\nu}$ are as follows:
\begin{align*}
	E &= h \cdot \nu \\
	\nu &= c/ \lambda \\
	\bar{\nu} &= 1/\lambda,
\end{align*}
where $h$ is the Planck's constant.
%In words: shorter wavelength (higher frequency) photons are more energetic.
In practice the spectrum of \gls{em} waves is sectioned into different ranges (\td{see figure?});
from high to low energy: X-ray, \gls{uv}, \gls{vis}, (near, middle and far) \gls{ir}, microwaves and radio waves. 
\td{with number?}
X-rays interact with core electrons, \gls{uv}\gls{vis} with valence electrons, \gls{ir} with molecular vibrations, microwaves with molecular rotations and radio with electron and nuclear spins. 
%Molecular vibrations can be separated in valence and deformation vibrations.
%
A molecule has $F=3N$ ($N$ number of atoms) degrees of freedom, including translational $F_T=3$ and rotational $F_R=3$ (2 for linear molecules) movements. 
%
The number of vibrations can therefore calculated as 
\begin{align*}
	F_V &= 3N - F_T - F_R = 3N - 6 \\
	F_V &= 3N - F_T - F_R = 3N - 5 \textrm{ (for linear molecules)}.
\end{align*}
Vibrations are classified in valence vibrations (change of bond length) and deformation (change of bond angle) vibrations\cite{Melker2006}. 
Only vibrations that change the dipole moment of the molecule are \gls{ir} active.

@@

\paragraph{(Fourier Transform) Infrared spectrometer}
 A ceramic material (Nernst glower) is heated to around \oc{1600} as light source. 
 In the two-beam-spectrometer the light is split, sent through the sample and a reference and alternately sent through a monochromator to a detector (thermocouple). 
%
In the \gls{ft}\gls{ir} spectrometer the beam is sent through the sample, split and 
reflected from a static and from a moving mirror, recombined and detected by a photo 
multiplier (a device which transforms photons into electrical signals). 
How the two beams will interfere upon recombination depends on the optical path difference (also called retardation) of the two light beams.
\td{In a \gls{ft}\gls{ir} spectrometer the reference has to be measured before the sample, individually}

\td{FREE WRITING:}
Absorbance per din 1349: $A(\lambda) = \log{\frac{\phi_{in}}{\phi_{ex}}}$ and transmission $\tau =T=D= \phi_{ex}/\phi_{in}$
The absorbance intensity is dependent on wave length and molecule structure. 
%\td{Frank-Condon rules, spin verbot and symmetrie verbot are ausschlaggebend für the resulting spectrum. }
%differences to \gls{uv}\gls{vis}: transmission instead of absorbance, higher energy left instead right in plot, base line on top instead of bottom.
When the refractive index of two layers differ, \gls{ir} can be used to measure the thickness\cite{Dumin1967}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Machine Learning}
\subsubsection{History}
some text to test
\subsubsection{different kinds} 
supervised vs unsupervised
classification (discrete) vs regression
\subsubsection{Particle Swarm Optimization}
\subsubsection{Princlipal Component Analysis}
reinforcement learning could also have been a nice option
\subsubsection{Linear Regression}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Infrared Absorption and Spectroscopy}
%%% WHAT? 
\Gls{ir} spectroscopy is a molecular spectroscopic method using interactions of \gls{ir} light (wavelengths $\lambda$ of \num{e-3} to \num{e-6}\m{}
or wave numbers $\bar{\nu}$ of 500 to \pcm{4000} ) with molecules. \cite{Schwedt2008}
In general, light is described as periodic \gls{em} wave 
which - in vacuum - moves with the speed of light ($c = \mps{299792458}$).
The relation of energy~$E$ of a photon, its frequency~$\nu$, wavelength~$\lambda$ and wave number~$\bar{\nu}$ are as follows:
\begin{align*}
	E &= h \cdot \nu \\
	\nu &= c/ \lambda \\
	\bar{\nu} &= 1/\lambda,
\end{align*}
where $h$ is the Planck's constant.
%In words: shorter wavelength (higher frequency) photons are more energetic.
In practice the spectrum of \gls{em} waves is sectioned into different ranges (\td{see figure?});
from high to low energy: X-ray, \gls{uv}, \gls{vis}, (near, middle and far) \gls{ir}, microwaves and radio waves. 
\td{with number?}
X-rays interact with core electrons, \gls{uv}\gls{vis} with valence electrons, \gls{ir} with molecular vibrations, microwaves with molecular rotations and radio with electron and nuclear spins. 
%Molecular vibrations can be separated in valence and deformation vibrations.
%
A molecule has $F=3N$ ($N$ number of atoms) degrees of freedom, including translational $F_T=3$ and rotational $F_R=3$ (2 for linear molecules) movements. 
%
The number of vibrations can therefore calculated as 
\begin{align*}
	F_V &= 3N - F_T - F_R = 3N - 6 \\
	F_V &= 3N - F_T - F_R = 3N - 5 \textrm{ (for linear molecules)}.
\end{align*}
Vibrations are classified in valence vibrations (change of bond length) and deformation (change of bond angle) vibrations\cite{Melker2006}. 
Only vibrations that change the dipole moment of the molecule are \gls{ir} active.

@@

\paragraph{(Fourier Transform) Infrared spectrometer}
 A ceramic material (Nernst glower) is heated to around \oc{1600} as light source. 
 In the two-beam-spectrometer the light is split, sent through the sample and a reference and one of the two beams is alternately sent through a monochromator to a detector (\td{thermocouple}). 
%
In the \gls{ft}\gls{ir} spectrometer the beam is sent through the sample, split and 
reflected from a static and from a moving mirror, recombined and detected by a photo 
multiplier (a device which transforms photons into electrical signals). 
How the two beams will interfere upon recombination depends on the optical path difference (also called retardation) of the two light beams\cite{Schwedt2008}.
In a \gls{ft}\gls{ir} spectrometer the reference has to be measured before the sample.
%
When the refractive index of two layers differ, \gls{ir} can be used to measure the thickness\cite{Dumin1967} of optical less dense material.

%\td{Frank-Condon rules, spin verbot and symmetrie verbot are ausschlaggebend für the resulting spectrum. }
%differences to \gls{uv}\gls{vis}: transmission instead of absorbance, higher energy left instead right in plot, base line on top instead of bottom.

\td{QUESTIONS: 
	how does detector work? two different for UVVis and MIR
	IR around page 45;
The absorbance intensity is dependent on wave length and molecule structure. 
Absorbance per din 1349: $A(\lambda) = \log{\frac{\phi_{in}}{\phi_{ex}}}$ and transmission $\tau =T=D= \phi_{ex}/\phi_{in}$
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Machine Learning}
\subsubsection{History}
find cool examples like in https://pubs.rsc.org/en/content/articlehtml/2019/sc/c9sc01742a
noteable mentions: GAN, language processing, self driving cars, image recognition, playing board games (and beating humans). 
See protocoll
dall-e 2 \cite{Marcus2022}
\subsubsection{different kinds} 
supervised vs unsupervised
classification (discrete) vs regression
\subsubsection{Particle Swarm Optimization}
\subsubsection{Princlipal Component Analysis}
reinforcement learning could also have been a nice option
\subsubsection{Linear Regression}
